---
output: word_document
---
#install.packages("rmarkdown")
#library("rmarkdown")

READING CREDSCO.CSV. NOTE: Change the path of the file for the proper one in your computer. 

Remember that subfolders must be indicated by "/" and not by "\"

```{r}
setwd("../Original_Dataset");
dd <- read.csv("Practica.csv",header=T, sep=";");
#setwd("../Original_Dataset/Other_Datasets"); if we want to see after preprocessing
#dd <- read.csv("Practica_processada.csv", header=T, sep=";");
```
 read.csv("/Users/alejandro/Desktop/Uni/4o/MD/Data-Mining/Practica.csv",header=T, sep=";");

Set the folder where the word file is going to be generated
```{r}
setwd("/Users/alejandro/Desktop/Uni/4o/MD/Data-Mining/")
```  

Check the type of the R object created for the dataset

```{r}            
class(dd)
```

i sense incloure la instruccio r en el document final seria 

```{r, echo=FALSE}            
class(dd)
```

Get dimensions of the dataset
````{r}
dim(dd)
n<-dim(dd)[1]
K<-dim(dd)[2]

n
K
```
Check the variables 

```{r}
names(dd)
```


Basic descriptive analysis for numerical variables
```{r, echo=FALSE}
listOfColors<-rainbow(39)

par(ask=TRUE)

for(k in 1:K){
  print(paste("variable ", k, ":", names(dd)[k] ))
  if (!is.numeric(dd[,k])){ 
    frecs<-table(as.factor(dd[,k]), useNA="ifany")
    proportions<-frecs/n
    #ojo, decidir si calcular porcentages con o sin missing values
    pie(frecs, cex=0.6, main=paste("Pie of", names(dd)[k]))
    barplot(frecs, las=3, cex.names=0.7, main=paste("Barplot of", names(dd)[k]), col=listOfColors)
    print(paste("Number of modalities: ", length(frecs)))
    print("Frequency table")
    print(frecs)
    print("Relative frequency table (proportions)")
    print(proportions)
    print("Frequency table sorted")
    print(sort(frecs, decreasing=TRUE))
    print("Relative frequency table (proportions) sorted")
    print(sort(proportions, decreasing=TRUE))
   }else{
    hist(dd[,k], main=paste("Histogram of", names(dd)[k]))
    boxplot(dd[,k], horizontal=TRUE, main=paste("Boxplot of", names(dd)[k]))
    print("Extended Summary Statistics")
    print(summary(dd[,k]))
    print(paste("sd: ", sd(dd[,k], na.rm=TRUE)))
    print(paste("vc: ", sd(dd[,k], na.rm=TRUE)/mean(dd[,k], na.rm=TRUE)))
   }
}
par(ask=FALSE)
```
